Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-03-14 doc/mc-paper.tex
start paper section on the verified checker
Fixed reference
merge

Each input clause deletion can be done as a single RUP step.  The
proof generator builds a sequence of hints from among the defining
clauses of the POG nodes via a single, bottom-up pass through the
graph.  The RUP deletion proof for input clause $C$ effectively proves that any
total assignment $\assign$ that does not satisfy $C$ will yield
$\assign(r) = 0$.  It starts with the set of literals
$\{ \obar{\lit} | \lit \in C\}$, describing the required condition for
assignment $\assign$ to falsify clause $C$.
It then
adds literals via unit propagation until a
conflict arises.    Unit literal $r$ gets
added right away, setting up a potential conflict.

>>>>

Each input clause deletion can be done as a single RUP step.  The
proof generator builds a sequence of hints from among the defining
clauses of the POG nodes via a single, bottom-up pass through the
graph.  The RUP deletion proof for input clause $C$ effectively proves that any
total assignment $\assign$ that does not satisfy $C$ will yield
$\assign(r) = 0$.  It starts with the set of literals
$\{ \obar{\lit} \mid \lit \in C\}$, describing the required condition for
assignment $\assign$ to falsify clause $C$.
It then
adds literals via unit propagation until a
conflict arises.    Unit literal $r$ gets
added right away, setting up a potential conflict.
